---
title: "Mark Project: First Draft"
author: "Shervin Bukhari^[Corresponding author: shervin.bukhari@psykologi.uio.no, Forskningsveien 3A, Harald Schjelderups hus, 0373 Oslo] [^PSI] [^NORMENT] [^UU], Mark Thompson[^UK] , Elisa de Mello e Souza Meth[^UU] , Christian Benedict[^UU] "
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document:
    extra_dependencies: ["float","flafter"]
  word_document: default
  html_document: default
---
[^PSI]: Department of Psychology, University of Oslo, Oslo, Norway
[^UU]: Department of Surgical Sciences, Sleep Science Laboratory, Uppsala University, Uppsala, Sweden
[^NORMENT]:Norwegian Centre for Mental Disorders Research (NORMENT), Oslo University Hospital, Oslo, Norway.
[^UK]:University of East Anglia, Norwich, United Kingdom

# Introduction

# Methods


```{r setup, include=FALSE, echo=FALSE}
# SETUP AND LOAD PACKAGES

knitr::opts_chunk$set(fig.width=6, fig.height=3, fig.path='figs/',
                      echo=FALSE, warning=FALSE, message=FALSE, fig.pos = "!H", out.extra = "", dpi=300)
library(knitr)
library(plyr)
library(dplyr)
library(readxl)
library(ggplot2)
library(rmarkdown)
library(cowplot)
library(readr)
library(forcats)
library(corrplot)
library(plotrix)
library(nlme)
library(lme4)
library(lmerTest)
library(stargazer)
library(ggpubr)
library(ggprism)
library(RColorBrewer)
library(sjPlot)
library(htmlTable)
library(emmeans)
library(metan)
# LOAD ALL DATA FILES (TIMELINE, SURVEY, KSSPANAS + PVT)
timeline<-read_xlsx("/home/shervin/Documents/GitStuff/Uppsala_MTfacestudy/timeline.xlsx")
dt<-read_xlsx("/home/shervin/Documents/GitStuff/Uppsala_MTfacestudy/MTdata_workfile.xlsx", sheet="Organized")
KSS_data <- read_xlsx("/home/shervin/Documents/GitStuff/Uppsala_MTfacestudy/KSS_PANAS_MT.xlsx")
PVT_data <- read_xlsx("/home/shervin/Documents/GitStuff/Uppsala_MTfacestudy/MTPVT_res.xlsx")

# Read survey response data from .xlsx sheet organized into long-format. Verified to contain correct data with "Processing_data.R" script.
dt$PicOrder <- as.numeric(dt$PicOrder) 
# adding a column for naps taken so that we can use this as a factor
dt<-dt %>% mutate(naps_taken = 
case_when(PicOrder <= 3 ~ "0",
          PicOrder >= 4 & PicOrder <= 6  ~  "1",
          PicOrder >= 7 & PicOrder <= 9 ~ "2",
          PicOrder >= 10 & PicOrder <= 11 ~ "3")
             )
#Calculate hours since last sleep
dt<- dt %>% mutate(hrsincesleep =
case_when(
                  Elapsed_Time == 0 ~ 2,
                  Elapsed_Time == 13.083 ~ 14.083,
                  Elapsed_Time == 25 ~ 27,
                  Elapsed_Time == 38.583 ~ 40.583,
                  Elapsed_Time == 48.65 ~ 4.05,
                  Elapsed_Time == 60.916 ~ 16.55,
                  Elapsed_Time == 73.366 ~ 29.98,
                  Elapsed_Time == 95.833 ~ 8.133,
                  Elapsed_Time == 108.416 ~ 20.72,
                  Elapsed_Time == 123.166 ~ 35.4,
                  Elapsed_Time == 133.666 ~ 2.663,
                  Elapsed_Time == 141.566 ~ 10.53))
                   

#Add a binary variable for if he had drunk coffee or not - after 111 hours.
dt$Caffeine<- if_else(dt$Elapsed_Time >= 111.7, 1,0)


#For each photograph, add the closest KSS and PVT measure data to dt


#SET COLOR PALETTE
palette=c("#FE9929","#08306B")#"#CC4C02","#FED98E" "#FE9929" 
###Exclude invalid responses from survey data

#Exclude responses taking more than 10 minutes (as per instructions)
dt<-dt %>% filter(600>dt$`Duration (in seconds)`) 
#Exclude responses that are not "No" to if they have done the study before
dt<-dt %>%filter(grepl('No',`survey_before`))
#Exclude responses with fraud score above threshold >=30
dt <- dt %>% filter(30>=dt$Q_RelevantIDFraudScore)
#Exclude responses with ID duplicate =true (likely duplicate)
dt<-dt %>% filter(!grepl('true',`Q_RelevantIDDuplicate`))
#Exclude >=75 duplicate scores (likely duplicate)
dt %>% filter(75>=dt$Q_RelevantIDDuplicateScore)
#Exclude if sex is not male or female
dt<-dt %>%filter(grepl('Male|Female',`Sex`))
#Make variables into correct format for analysis and plotting
dt$Age<-as.numeric(dt$Age)
dt$Sex<-factor(dt$Sex)
dt$Gender<-factor(dt$Gender)
dt$Sleeplastnight<-as.numeric(dt$Sleeplastnight)
dt$VAS_sleepy <- as.numeric(dt$VAS_sleepy)
# Rating variables
dt$Marks_age <- as.numeric(dt$Marks_age)
dt$VAS_stressed <- as.numeric(dt$VAS_stressed)
dt$VAS_tired <- as.numeric(dt$VAS_tired)
dt$VAS_attractive <- as.numeric(dt$VAS_attractive)
dt$VAS_healthy <- as.numeric(dt$VAS_healthy)
dt$VAS_resemblance <- as.numeric(dt$VAS_resemblance)
dt$VAS_trustworthy <- as.numeric(dt$VAS_trustworthy)
dt$VAS_scary <- as.numeric(dt$VAS_scary)
dt$survey_before<-factor(dt$survey_before)
dt$know_him <- factor(dt$know_him)
dt$Elapsed_Time <- as.numeric(dt$Elapsed_Time)
dt$Circadian_Phase <-factor(dt$Circadian_Phase)
dt$naps_taken <-factor(as.factor(dt$naps_taken))
dt$Circadian_Phase<-as.factor(dt$Circadian_Phase)

#
PVT_data$Session=factor(PVT_data$Session)
PVT_data$Circadian_Phase=factor(PVT_data$Circadian_Phase)
PVT_data$Day=factor(PVT_data$Day)

KSS_data$Session=factor(KSS_data$Session)
KSS_data$PHASE=factor(KSS_data$PHASE)
KSS_data$Day=factor(KSS_data$Day)
```
# Results
```{r,echo=FALSE}
# Plot Age Distribution for whole survey sample
p<-ggplot(dt, aes(x=Age)) + 
  geom_histogram(color="black", fill="white", bins=100) +
  geom_density(alpha=0.7) +
  labs(x="Rater Age", y="Count")
p

p_absage<-ggplot(dt, aes(x=absage_diff)) + 
  geom_histogram(color="black", fill="white", bins=100) +
  geom_density(alpha=0.7) +
  labs(x="Rater Absolute Age Difference", y="Count")
p_absage

```
More descriptive plots of survey data
```{r,echo=FALSE}
p2<-ggplot(data=dt, aes(x=Sex), xName="Sex", fill="white") +
  geom_bar()
p2

p3 <- ggplot(data=dt, aes(x=Gender),xName="Gender", fill="white")+
  geom_bar()
p3

p4 <- ggplot(data=dt, aes(x=Sleeplastnight))+
geom_histogram(color="black", fill="white", bins=20)+
labs(x="Rater Sleep Previous Night")
p4

p5<-ggplot(data=dt, aes(x=VAS_sleepy))+
geom_histogram(color="black", fill="white", bins=10)+
labs(x="Rater Sleepiness")
p5
```

```{r,include = FALSE, echo = FALSE}

#Compute mean and sd for all response variables splitting by Elapsed_Time
# Create baseline corrected variable for each measure by subtracting mean of first time point.

markage<- dt %>% group_by(Elapsed_Time, hrsincesleep, Circadian_Phase) %>% summarise(m_markage=mean(Marks_age), sd_markage =sd(Marks_age), se_markage=std.error(Marks_age))

attr<-dt %>% group_by(Elapsed_Time, Circadian_Phase) %>% summarise(m_attr=mean(VAS_attractive), sd_attr =sd(VAS_attractive),se_attr=std.error(VAS_attractive))

hlthy<- dt %>% group_by(Elapsed_Time, hrsincesleep, Circadian_Phase) %>% summarise(m_hlthy=mean(VAS_healthy), sd_hlthy =sd(VAS_healthy), se_hlthy=std.error(VAS_healthy))

strss<-dt %>% group_by(Elapsed_Time, Circadian_Phase) %>% summarise(m_strss=mean(VAS_stressed), sd_strss =sd(VAS_stressed),se_strss=std.error(VAS_stressed))

scry<-dt %>% group_by(Elapsed_Time,hrsincesleep,  Circadian_Phase) %>% summarise(m_scry=mean(VAS_scary), sd_scry =sd(VAS_scary), se_scry=std.error(VAS_scary))

rsmblc<-dt %>% group_by(Elapsed_Time,hrsincesleep,  Circadian_Phase) %>% summarise(m_rsmblc=mean(VAS_resemblance), sd_rsmblc =sd(VAS_resemblance), se_rsmblc=std.error(VAS_resemblance))

trd <-dt %>% group_by(Elapsed_Time,hrsincesleep,  Circadian_Phase) %>% summarise(m_trd=mean(VAS_tired), sd_trd =sd(VAS_tired), se_trd=std.error(VAS_tired))

trstwrthy <-dt %>% group_by(Elapsed_Time, Circadian_Phase) %>% summarise(m_trstwrthy=mean(VAS_trustworthy), sd_trstwrthy =sd(VAS_trustworthy), se_trstwrthy=std.error(VAS_trustworthy))

dt$Marks_age_minus <-dt$Marks_age-47.92574
dt$VAS_attractive_minus <-dt$VAS_attractive-2.881188 #mean attractiveness at 0
dt$VAS_healthy_minus <- dt$VAS_healthy-4.440000 # mean healthy at 0 
dt$VAS_scary_minus<- dt$VAS_scary-2.920792 #mean scariness at 0
dt$VAS_stressed_minus<-dt$VAS_stressed-5.574257 #mean stressed at 0
dt$VAS_tired_minus<-dt$VAS_tired-5.712871 #mean tired at 0
dt$VAS_trustworthy_minus<-dt$VAS_trustworthy-5.257426 #mean trustworthy at 0
dt <- dt %>% mutate(Caffeine = if_else(Elapsed_Time > 111, 1, 0))
dt_bl <- subset(dt,Elapsed_Time>0)

markage_bl<- dt_bl %>% group_by(Elapsed_Time,hrsincesleep, Circadian_Phase) %>% summarise(m_markage=mean(Marks_age_minus), sd_markage =sd(Marks_age_minus), se_markage=std.error(Marks_age_minus)) 

attr_bl<- dt_bl %>% group_by(Elapsed_Time,hrsincesleep,  Circadian_Phase) %>% summarise(m_attr=mean(VAS_attractive_minus), sd_attr =sd(VAS_attractive_minus), se_attr=std.error(VAS_attractive_minus))
                                                                              
hlthy_bl<- dt_bl %>% group_by(Elapsed_Time, hrsincesleep, Circadian_Phase) %>% summarise(m_hlthy=mean(VAS_healthy_minus), sd_hlthy =sd(VAS_healthy_minus), se_hlthy=std.error(VAS_healthy_minus)) 

scry_bl<- dt_bl %>% group_by(Elapsed_Time, hrsincesleep,Circadian_Phase) %>% summarise(m_scry=mean(VAS_scary_minus), sd_scry =sd(VAS_scary_minus), se_markage=std.error(VAS_scary_minus)) 

strss_bl<- dt_bl %>% group_by(Elapsed_Time, hrsincesleep, Circadian_Phase) %>% summarise(m_strss=mean(VAS_stressed_minus), sd_strss =sd(VAS_stressed_minus), se_strss=std.error(VAS_stressed_minus)) 

trd_bl<- dt_bl %>% group_by(Elapsed_Time, hrsincesleep, Circadian_Phase) %>% summarise(m_trd=mean(VAS_tired_minus), sd_trd =sd(VAS_tired_minus), se_trd=std.error(VAS_tired_minus)) 

trstwrthy_bl<- dt_bl %>% group_by(Elapsed_Time, hrsincesleep, Circadian_Phase) %>% summarise(m_trstwrthy=mean(VAS_trustworthy_minus), sd_trstwrthy =sd(VAS_trustworthy_minus), se_trstwrthy=std.error(VAS_trustworthy_minus)) 


```
Plotting distribution of ratings, plain - not split by any individual factor or condition
```{r Descriptive plots, echo=FALSE}
d_age <-ggplot(dt, aes(x=Marks_age))+
  geom_histogram(color="black", fill="white", bins=100)+
  labs(x="Marks estimated age",y="Count")
d_age

d_trd <-ggplot(dt, aes(x=VAS_tired))+
  geom_histogram(color="black", fill="white", bins=10)+
  labs(x="Marks rated tiredness",y="Count")
d_trd

d_hlthy <-ggplot(dt, aes(x=VAS_healthy))+
  geom_histogram(color="black", fill="white", bins=10)+
    labs(x="Marks rated healthiness",y="Count")
d_hlthy

d_attr <-ggplot(dt, aes(x=VAS_attractive))+
  geom_histogram(color="black", fill="white", bins=10)+
    labs(x="Marks rated attractiveness",y="Count")
d_attr

d_trstwrthy <-ggplot(dt, aes(x=VAS_trustworthy))+
  geom_histogram(color="black", fill="white", bins=10)
d_trstwrthy


d_strss <-ggplot(dt, aes(x=VAS_stressed))+
geom_histogram(color="black", fill="white", bins=10)
    labs(x="Marks rated stress",y="Count")
d_strss


d_scry <-ggplot(dt, aes(x=VAS_scary))+
geom_histogram(color="black", fill="white", bins=10)
    labs(x="Marks rated scariness",y="Count")
d_scry

d_rsmblc<-ggplot(dt, aes(x=VAS_resemblance))+
  geom_histogram(color="black", fill="white", bins=10)+
#  geom_density(color="black", fill="white", alpha=0.5)
    labs(x="Marks rated resemblance",y="Count")
d_rsmblc

```
Raincloud plots baseline corrected
```{r,raincloud_plots, echo=FALSE}

# Mark's Age baseline corrected
raincloud_age_bl<-ggplot(dt_bl, aes(x = Elapsed_Time, y = Marks_age_minus, group = Elapsed_Time, colour=Circadian_Phase))+
#  geom_flat_violin(aes(fill = Elapsed_Time),position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = TRUE, colour = NA,alpha=0.6)+
  geom_point(aes(x = as.numeric(Elapsed_Time)-2, y = Marks_age_minus),position = position_jitter(seed=1,width = 2),size = 3, shape = 20, alpha=.3)+
  geom_boxplot(aes(x = as.numeric(Elapsed_Time), y = Marks_age_minus, group = Elapsed_Time), width = 7, outlier.shape = NA,alpha=0.4)+
geom_errorbar(data = markage_bl, aes(x = as.numeric(Elapsed_Time)+.1, y = as.numeric(m_markage), ymin = as.numeric(m_markage-sd_markage), ymax = as.numeric(m_markage+sd_markage), width = 5), size=1 )+
geom_point(data = markage_bl, aes(x = as.numeric(Elapsed_Time)+.1, y = as.numeric(m_markage)), shape = 15)+
  geom_vline(xintercept=c(42.620, 85.950, 129.300), size=.75)+
#  geom_hline(yintercept=c(48), size=1, linetype=2)+
ggtitle("")+
labs(x="Time (Hrs)",y="Estimated Age")+
theme_bw()+
theme(legend.position = "right",legend.title = element_blank(),legend.key = element_blank(),panel.border = element_blank(), panel.background = element_blank())+
scale_colour_manual(values=palette)
raincloud_age_bl

raincloud_trd_bl<-ggplot(dt_bl, aes(x = Elapsed_Time, y = VAS_tired_minus, group = Elapsed_Time, colour=Circadian_Phase))+
#  geom_flat_violin(aes(fill = Elapsed_Time),position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = TRUE, colour = NA,alpha=0.6)+
  geom_point(aes(x = as.numeric(Elapsed_Time)-2, y = VAS_tired_minus),position = position_jitter(seed=1,width = 2),size = 3, shape = 20, alpha=.3)+
  geom_boxplot(aes(x = as.numeric(Elapsed_Time), y = VAS_tired_minus, group = Elapsed_Time), width = 7, outlier.shape = NA,alpha=0.4)+
geom_errorbar(data = trd_bl, aes(x = as.numeric(Elapsed_Time)+.1, y = as.numeric(m_trd), ymin = as.numeric(m_trd-sd_trd), ymax = as.numeric(m_trd+sd_trd), width = 5), size=1 )+
geom_point(data = trd_bl, aes(x = as.numeric(Elapsed_Time)+.1, y = as.numeric(m_trd)), shape = 15)+
  geom_vline(xintercept=c(42.620, 85.950, 129.300), size=.75)+
#  geom_hline(yintercept=c(48), size=1, linetype=2)+
ggtitle("")+
labs(x="Time (Hrs)",y="Tiredness")+
theme_bw()+
theme(legend.position = "right",legend.title = element_blank(),legend.key = element_blank(),panel.border = element_blank(), panel.background = element_blank())+
scale_colour_manual(values=palette)
raincloud_trd_bl


boxplot_trd<- ggplot(dt_bl, aes(x = Elapsed_Time, y = VAS_tired_minus, group = Elapsed_Time, colour=Circadian_Phase))+geom_boxplot(aes(x = as.numeric(Elapsed_Time), y = VAS_tired_minus, group = Elapsed_Time), width = 7, outlier.shape = NA,alpha=0.4)+
geom_errorbar(data = trd_bl, aes(x = as.numeric(Elapsed_Time)+.1, y = as.numeric(m_trd), ymin = as.numeric(m_trd-sd_trd), ymax = as.numeric(m_trd+sd_trd), width = 5), size=1 )+
geom_point(data = trd_bl, aes(x = as.numeric(Elapsed_Time)+.1, y = as.numeric(m_trd)), shape = 15)+
  geom_vline(xintercept=c(42.620, 85.950, 129.300), size=.75)+
#  geom_hline(yintercept=c(48), size=1, linetype=2)+
ggtitle("")+
labs(x="Time (Hrs)",y="Tiredness")+
theme_bw()+
theme(legend.position = "right",legend.title = element_blank(),legend.key = element_blank(),panel.border = element_blank(), panel.background = element_blank())+
scale_colour_manual(values=palette)
boxplot_trd

```

Cross correlation matrix for all ratings, not split by time.
```{r, correlation plot, echo=FALSE}
corr_dt <- dt %>% select(VAS_sleepy,VAS_stressed,VAS_tired,VAS_trustworthy,VAS_attractive,VAS_attractive,VAS_healthy,VAS_scary,VAS_resemblance, Elapsed_Time, Marks_age)
corrmat <- cor(corr_dt)
cp_raw<-corrplot(corrmat, title="",type="lower" ,    method='color',    addCoef.col = "black", tl.col="black", tl.srt=45, sig.level = 0.005, insig = "blank", number.cex = 0.5)
```

Linear model for Age
```{r, echo=FALSE}
## Check older versions of script for different models
# VAS sleepiness has better predictive power than hours Slept
# Age is better than absolute age difference or age difference
model_age1a<- lm(data=dt, Marks_age~Age + Sex + VAS_sleepy + Elapsed_Time) 
model_age1b<- lm(data=dt, Marks_age~Age + Sex + VAS_sleepy + Circadian_Phase) 
summary(model_age1a)
summary(model_age1b)
model_age1c<-lm(data=dt, Marks_age~Age + Sex + VAS_sleepy + Elapsed_Time + Circadian_Phase)
model0_age<-lm(data=dt, Marks_age~Age + Sex + VAS_sleepy + Elapsed_Time + Circadian_Phase) 
summary(model0_age)
#Neither Elapsed Time or Circadian Phase are significant on their own
model_age2<-lm(data=dt,Marks_age~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time)

model_age4<-lm(data=dt,Marks_age~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)


model_age5<-lm(data=dt,Marks_age~Sex+Age+VAS_sleepy+Sleeplastnight+Elapsed_Time+Circadian_Phase+naps_taken)
summary(model_age5)

model_age6<-lm(data=dt,Marks_age~Sex+Age+VAS_sleepy+Sleeplastnight+Elapsed_Time+Elapsed_Time*VAS_sleepy)
summary(model_age6)

summary(model_age2)
#summary(model_age3)
summary(model_age4)
summary(model_age6)
summary(model_age1c)
anova(model_age4)
emmeans(model_age4, pairwise ~Elapsed_Time*naps_taken)
```   
Generalized Linear Model for Tiredness, Attractiveness, Health
```{r, echo=FALSE}
#TIRED
model0_trd<-lm(data=dt, VAS_tired~Age + Sex + VAS_sleepy + Elapsed_Time + Circadian_Phase) 
summary(model0_trd)
model1_trd <-glm(data=dt, VAS_tired~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time)
summary(model1_trd)
model2_trd<-glm(dat=dt, VAS_tired~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)
summary(model2_trd)


model0_attr<-lm(data=dt, VAS_attractive~Age + Sex + VAS_sleepy + Elapsed_Time + Circadian_Phase) 
summary(model0_attr)
model1_attr<-glm(data=dt, VAS_attractive~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time)
summary(model1_attr)
model2_attr<-glm(dat=dt, VAS_attractive~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)
summary(model2_attr)

model0_hlthy<-lm(data=dt, VAS_healthy~Age + Sex + VAS_sleepy + Elapsed_Time + Circadian_Phase) 
summary(model0_hlthy)
model1_hlthy<-glm(data=dt, VAS_healthy~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time)
summary(model1_hlthy)
model2_hlthy<-glm(data=dt, VAS_healthy~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)
summary(model2_hlthy)

model1_stressed<-glm(data=dt, VAS_stressed~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time)
summary(model1_stressed)
model2_stressed<-glm(data=dt,VAS_stressed~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)
summary(model2_stressed)


model1_scary<-glm(data=dt, VAS_scary~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time)
summary(model1_scary)
model2_scary<-glm(data=dt,VAS_scary~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)
summary(model2_scary)

model0_trustworthy<-glm(data=dt, VAS_trustworthy~Sex+Age+VAS_sleepy+Circadian_Phase+Elapsed_Time+VAS_resemblance)
summary(model0_trustworthy)
model1_trustworthy<-glm(data=dt, VAS_trustworthy~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+VAS_resemblance)
summary(model1_trustworthy)
model2_trustworthy<-glm(data=dt,VAS_trustworthy~Sex+Age+VAS_sleepy+naps_taken+Circadian_Phase+Elapsed_Time+VAS_resemblance+Circadian_Phase*Elapsed_Time+Elapsed_Time*naps_taken)
summary(model2_trustworthy)
```

#ANOVA OF NAPS
```{r}

dt_anova<- dt %>% mutate(before_after =
case_when(
                  Elapsed_Time == 38.583 ~ 0,
                  Elapsed_Time == 48.65 ~ 1,
                  Elapsed_Time == 73.366 ~ 0,
                  Elapsed_Time == 95.833 ~ 1,
                  Elapsed_Time == 123.166 ~ 0,
                  Elapsed_Time == 133.666 ~ 1))

naps_age<-aov(Marks_age~before_after+Age+Sex+VAS_sleepy+Elapsed_Time,dt_anova)
naps_age<-lm(Marks_age~before_after+Age+Sex+VAS_sleepy+Elapsed_Time+naps_taken,dt_anova)
naps_trd<-aov(VAS_tired~before_after+Age+Sex+VAS_sleepy+Elapsed_Time,dt_anova)
naps_attr<-aov(VAS_attractive~before_after+Age+Sex+VAS_sleepy+Elapsed_Time,dt_anova)
naps_hlthy<-aov(VAS_healthy~before_after+Age+Sex+VAS_sleepy+Elapsed_Time,dt_anova)
naps_trstwrthy<-aov(VAS_trustworthy~before_after+Age+Sex+VAS_sleepy+Elapsed_Time+VAS_resemblance,dt_anova)

TukeyHSD(naps_age, naps_taken)

```

Plotting Model results
```{r}
set_theme(base=theme_bw(), axis.ticksize.x = 1.5, axis.ticksize.y= 1.5,axis.title.size = 2.5, title.size =0, panel.bordercol = "white")
plot_age<- plot_model(model_age2, type="pred", terms="Elapsed_Time", axis.title = c("Time (Hrs)", "Estimated Age")) 
plot_age
plot_model(model_age2)
plot_tired<- plot_model(model1_trd, type="pred", terms="Elapsed_Time", axis.title = c("Time (Hrs)", "Tiredness")) 
plot_healthy<-plot_model(model1_hlthy, type="pred", terms="Elapsed_Time", axis.title = c("Time (Hrs)", "Healthiness"))
plot_tired
plot_healthy
ggarrange(plot_tired,plot_healthy,labels="A","B", ncol = 2, nrow = 2)

plot_model(model2_trustworthy, type="pred",terms="Elapsed_Time", axis.title = c("Time (Hrs)", "Trustworthyness"))

```
#Make Tables
```{r}
outp1<-tab_model(model_age2)#,model_age4)

outp2<-tab_model(model1_attr,model1_hlthy,model1_trd)

outp3<-tab_model(model2_attr,model2_hlthy,model2_trd)

outp4<-tab_model(model1_trustworthy)#,model2_trustworthy)

pvalues<-c(summary(model_age2)$coefficients[,4],summary(model1_attr)$coefficients[,4],summary(model1_hlthy)$coefficients[,4],summary(model1_trd)$coefficients[,4],summary(model1_trustworthy)$coefficients[,4])

pvalues<-p.adjust(pvalues, method = "fdr", n=length(pvalues))
pvalues

p_anova<-c(summary(naps_age)[[1]][1:6,5], summary(naps_trd)[[1]][1:6,5],summary(naps_attr)[[1]][1:6,5],summary(naps_hlthy)[[1]][1:6,5],summary(naps_trstwrthy)[[1]][1:6,5])
p_anova<-p.adjust(p_anova, method = "fdr", n=length(p_anova))
```

```{r}
dt_anova<-subset(dt_anova, before_after== 0 | before_after== 1)
t<-ggplot(data = dt_anova, aes(x=before_after, y =Marks_age , colour = before_after)) + 
  geom_point()


age_naps_eff<- dt_anova %>%group_by(before_after) %>% summarise(m=mean(Marks_age), s=sd(Marks_age))
hlthy_naps_eff<-dt_anova %>%group_by(before_after) %>% summarise(m=mean(VAS_healthy),s= sd(VAS_healthy))
```



